---
title: "Additional Plot Features"
author: 'w203: Statistics for Data Science'
output: github_document
---

From here on out, we're going to start working in **R Markdown Files**. These files let us weave code and explanation together. What you're reading right here is explanation -- this isn't actually run by the interpreter in the console. 

But, what you're seeing just below -- in a "chunk" set off by three bac-kticks -- is a code block. 

If you look at line 14, and run this line just as you would have if this were an .R file (it is a .Rmd file) what happens? 

```{r}
print('Hello world.')
```

Now, the result rather than being printed to the console is both printed in the console and in line with this code. One piece that you might have noticed is the curly braces after the first set of back-ticks. This is telling the interpreter that this is code that is written in the R languge. It is possible (though we won't do this for now) to write python, julia, c++ or other code within these chunks and have the interpreter evaluate them. 

Below, I'm going to write a chunk that I've called "setup" that is going to load libraries and set themes and set parameters for plots. I've also added extra arguments to this code chunk declaration -- `results = 'hide', warning=FALSE, message=FALSE`. These control how the chunk works, but let's not dig **too** far into that just yet. 

```{r setup, results='hide', warning=FALSE, message=FALSE}
library(tidyverse)
library(ggplot2)
theme_set(theme_minimal())
knitr::opts_chunk$set(dpi = 200)
```

In this chunk, which I've called "load data" I'm going to load the data, and then create the date field that we've used all along. 

```{r load data}
squirrel_subset <- read_csv('./squirrels_subset.csv')
squirrel_subset <- squirrel_subset %>%
  mutate(date_f = as.Date.character(date, format = '%m%d%Y'))
```

Now, you can see below that I'm creating a section in the markdown space by starting the line with a "hash". If this were in a code chunk, it would comment out the line, but here in the markdown space, this will create a level-1 heading. Two hashes would create a level-2 heading (one further indent). 

# Data Reminder 

As a reminder, we're working with data that is from the "census of squirrels" in NYC's central park. 
Each row is an observation of a squirrel, and each observation has as much data as possible about the observation. 

## Previous Plots 

The last set of plots that we made with `geom_point()` were simple scatter plots where we passed: 

- The `long`; 
- The `lat`; and, 
- One other feature. 

```{r the old plot}
ggplot(data = squirrel_subset) + 
  aes(x = long, y = lat) + 
  geom_point() + 
  coord_quickmap()
```


# This plot 

For this plot, I'd like you to represent four data series in a single plot. Because each of these are information in the dataset that we want to control the way the plot is built, each of the series should go into the `aes()` funciton. 

1. The `long`; 
2. The `lat`; 
3. The `age`; 
4. The `primary_fur_color`. 

I'm sure you're wondering? What aestetic options are available to me? To look into this, let's look into the documentation for `geom_point()`, because the `geom_point()` inherits its aestetics from the `aes()` function. 

When you run the line below, your Rstudio should then open a help browser

```{r geom_point_help}
?geom_point()
```

I see several aesthetics listed: 

- x
- y 
- alpha, ... and many more. 

Before you start to build the plot -- think about what you might want to show -- you might go as far as to write down the plot that you want to create (as I've just suggested in the lecture) but that isn't strictly necessary because this is reasonably straightforward data. 
Once you know what you'd like to show, pass data series into these aesthetics until you have created a plot that you think does a good job of representing your idea. 

```{r}

```