---
title: ''
author: 'w203: Statistics for Data Science'
date: "8/13/2020"
output: github_document
---

```{r setup, results='hide', warning=FALSE, message=FALSE}
library(tidyverse)
```

```{r load data, results = 'hide', message=FALSE}
agencies <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-01-15/agencies.csv')
launches <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-01-15/launches.csv')
```

# Task 

Use the magrittr pipr `%>%` and the `filter()` verb to do the following work: 

## Launches in the 1980s

Find only the launches that occurred in the 1980s 

```{r}
launches %>% 
  filter(launch_year >= 1980) %>% 
  filter(launch_year < 1990)
```

Or, equivalently

```{r}
launches %>% 
  filter(launch_year >= 1980, launch_year < 1990)
```

## Launches by France 

Find only the launches that were conducted by France (`state_code == "F"` )

```{r}
launches %>% 
  filter(state_code == "F")
```

## Launches by France in the 1980s

Find only the launches by France that were conducted in the 1980s

```{r}
launches %>% 
  filter(launch_year >= 1980, launch_year < 1990, state_code == "F")
```

## Launches by France or Russia in the 1980s 

Find launches in the 1980s by either France or the Soviet Union

```{r}
launches %>% 
  filter(launch_year >= 1980, launch_year < 1990, state_code %in% c("F", "SU"))
```

