---
title: "Make A Data Set"
author: 'w203: Statistics for Data Science'
date: "8/14/2020"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)

ggplot2::diamonds
```

# Paste Farm Code 

Start by pasting the code that you wrote to create the farm animals below. 

```{r}
ID <- 1:300
animal <- c(rep('cow', 10), rep('sheep', 50), rep('goat', 40), rep('chicken', 70), rep('rabbit', 130))
petting_zoo <- rep('no', 300)
petting_zoo[animal == 'rabbit'] <- 'yes'

weight <- rep(NA, 300)
weight[animal == 'cow']     <- rnorm(n = 10, mean = 1000, sd = 100)
weight[animal == 'sheep']   <- rnorm(n = 50, mean = 100, sd = 2)
weight[animal == 'goat']    <- rnorm(n = 40, mean = 40, sd = 2)
weight[animal == 'chicken'] <- .2
weight[animal == 'rabbit']  <- NA

feed <- rep(NA, 300)

feed[animal == 'cow']     <- weight[animal == 'cow'] * .03   
feed[animal == 'sheep']   <- weight[animal == 'sheep'] *.02  
feed[animal == 'goat']    <- weight[animal == 'goat'] * .07
feed[animal == 'chicken'] <- weight[animal == 'chicken'] * .02
feed[animal == 'rabbit']  <- NA
```

## Combine into a dataset 

Now, combine all of these variables into a single dataset, called `tilden`. 

```{r}
tilden <- data.frame(
  ID, animal, petting_zoo, weight, feed
)
```


## Typecast 

Now do a little bit of mutating and type converting. 

- Since we know that each of the types of animals has a specific amount that they eat, let's label them "hungry boi" if they eat more than average; and "slender boi" if they eat less than average. (Sorry... I know this coding might be getting tedious!). 
- Make each of these relative to the mean within that animal type. 

```{r}
tilden %>%
  group_by(animal) %>%  
  mutate(hungry_slender = ifelse(weight > mean(weight), 'hungry boi', 'slender boi'))
```