---
title: "make_it_sparkle.Rmd"
author: 'w203: Statistics for Data Science'
output: github_document
---

```{r setup, results='hide', warning=FALSE, message=FALSE}
library(tidyverse)
library(ggplot2)
# install.packages('patchwork')
library(patchwork)

theme_set(theme_minimal())
knitr::opts_chunk$set(dpi = 200)
```

```{r load and mutate data}
squirrel_subset <- read.csv('squirrels_subset.csv')
squirrel_subset <- filter(squirrel_subset, !is.na(primary_fur_color))

squirrel_subset <- squirrel_subset %>%
  mutate(date_f = as.Date.character(date, format = '%m%d%Y'))
```

# Coding Task 

Suppose that you want to communicate to someone who has less context with the data. Set the `labs()` argument to include 

- A title 
- A subtitle 
- Descriptive Labels for the axes 
- A label for what the colors mean. 

Each of the labels should be in **plain spoken language** and should be in sentence case: 

- The first letter of the first work should be capitalized
- The rest of the letters should *not* be capitalized
- Everything should be a work that you can speak aloud -- i.e. **not** a variable name. 

```{r coding task}
squirrel_subset %>%  
  group_by(date_f, primary_fur_color) %>%  
  summarise(count_of_squirrels = n()) %>%  
  ggplot() + 
  aes(x = date_f, y = count_of_squirrels, color = primary_fur_color) + 
  stat_smooth(se = FALSE) + 
  labs(
    title = 'There are a lot of grey squirrels',
    subtitle = 'But, people are collecting data in later days',
    x = 'Date of observation', 
    y = 'Count of squirrels', 
    color = 'Primary Fur Color'
  )
```
