---
title: "Making Bar Plots"
author: 'w203: Statistics for Data Science'
output: github_document
---

```{r setup, results='hide', warning=FALSE, message=FALSE}
library(tidyverse)
library(ggplot2)
# install.packages('patchwork')
library(patchwork)

theme_set(theme_minimal())
knitr::opts_chunk$set(dpi = 200)
```

```{r load data}
squirrel_subset <- read.csv('squirrels_subset.csv')
```

```{r aggregate data}
squirrel_subset_by_color <- squirrel_subset %>%  
  group_by(primary_fur_color) %>%  
  summarise(count_by_color = n())
```

# Task 

Produce two identical plots that have the following characteristics: 

- On the x-axis the plots have the color of the squirrel fur
- On the y-axis the plots have a count of the nubmer of squirrels that have that color fur

However, make these plots in two ways: 

1. In one plot, use `geom_bar()` (and the appropriate dataset)
2. In the other plot, use `geom_col()` (and the appropriate dataset)

Note that the datsets will be different for each of the different geometries. 

```{r}

```