---
title: 'Mutating a New Varible'
author: 'w203: Statistics for Data Science'
date: "8/13/2020"
output: github_document
---

```{r setup, results='hide', warning=FALSE, message=FALSE}
library(tidyverse)
```

```{r load data, message=FALSE}
agencies <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-01-15/agencies.csv')
launches <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-01-15/launches.csv')
```

# Mutate Task 

- Using the `agencies` data, create a series of variables that contain the log of the `count` of launches. 

```{r}
agencies_log <- agencies %>% 
  mutate(count_log = log(count))

agencies_log
```

> But not that you don't *have* to assign this to a new object.

- Then, show only the columns that are called either `agency` or `contains()` the string "count". 

```{r}
agencies_log %>%  
  select(agency, contains('count'))
```

- Finally, `arrange()` these descending by `count`. 

```{r}
agencies_log %>%  
  select(agency, contains('count')) %>%  
  arrange(desc(count))
```

> HA! It looks as though the data came in the door arranged by count. However, I would **never** suggest relying on this. If you want the data arranged by count, write the code to do so. The upstream data that comes into your analysis could change; potentially without you knowing. 
> 
> If you want your data to have some particualr characteristic, you should write the code that makes it be so. 